\chapter{Appendices}

Here we will briefly describe the structure of the Github repository and how to install the project:

\section{Github Repo}
Github link: https://github.com/MatthewSloyan/final-year-applied-project-and-minor-dissertation
\begin{itemize}
    \item Chatbot: This folder contains the python flask server along with the AIML files. There is also a test Keras chatbot that was used during research.
    \item Dissertation: This folder contains all disseration material.
    \item Presentation: This folder contains the slide material along with a video presentation.
    \item Research: This folder contains all the research that was performed prier to development.
    \item UnityEngine: This folder contains the entire Unity side of the project. This includes all assets scripts etc.
\end{itemize}
\newpage
\section{How to Run}
Here we will explain how to download and install the project for the Oculus Quest:
\begin{enumerate}
    \item Download or clone the GitHub repo
    \item Add Unity 2019.2.6f1 to your Unity Hub. 
    \item Navigate to the "UnityEngine" and add the FinalYearProject folder to your Unity projects in Unity Hub.
    \item Launch the project.
    \item Once the project is open connect your Oculus Quest to your PC.
    \item Navigate to "File" then "Build Settings".
    \item Highlight Android under platforms and click "Switch Platform".
    \item With your Oculus Quest connected, click "Build and Run".
    \item The application will then be build and run on the Oculus.
\end{enumerate}

As the server is hosted on PythonAnywhere there is no need to make anymore change to connect to the server and it should connect by default.